---
output: html_document
editor_options: 
  chunk_output_type: console
---

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highcharter?color=brightgreen)](https://cran.r-project.org/package=highcharter)
[![CRAN downloads](http://cranlogs.r-pkg.org/badges/highcharter?color=brightgreen)](http://www.r-pkg.org/pkg/highcharter)
[![travis-status](https://api.travis-ci.org/jbkunst/highcharter.svg)](https://travis-ci.org/jbkunst/highcharter)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jbkunst/highcharter?branch=master&svg=true)](https://ci.appveyor.com/project/jbkunst/highcharter)
[![GitHub closed issues](https://img.shields.io/github/issues-raw/jbkunst/highcharter.svg)](https://github.com/jbkunst/highcharter/issues)
[![GitHub issues](https://img.shields.io/github/issues-closed-raw/jbkunst/highcharter.svg)](https://github.com/jbkunst/highcharter/issues)
[![Github Stars](https://img.shields.io/github/stars/jbkunst/highcharter.svg?style=social&label=Github)](https://github.com/jbkunst/highcharter)

<h1><div id="brand">h|1i|0g|3h|2c|1h|2a|1r|3t|2e|1r|2{rpackage}</div></h1> 


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(highcharter)
library(tidyverse)

hc_theme_index <- 
  hc_theme_smpl(
    plotOptions = list(
      series = list(showInLegend = FALSE),
      line = list(lineWidth = 1.2)
      ),
    xAxis = list(
      showLastLabel = FALSE,
      showFirstLabel = FALSE,
      endOnTick = FALSE,
      startOnTick = FALSE
      ),
    yAxis = list(
      showLastLabel = FALSE,
      showFirstLabel = FALSE,
      endOnTick = FALSE,
      startOnTick = FALSE
      ),
    tooltip = list(valueDecimals = 2)
  )


# example 1
data(mpg, package = "ggplot2")
mpg <- select(mpg, displ, hwy)
p1 <- hchart(
  mpg,
  "scatter",
  hcaes(x = displ, y = hwy, color = hwy),
  name = "Cars"
  ) %>%
  hc_add_theme(hc_theme_index)

# example 2
library(forecast)
p2 <- hchart(
  forecast(ets(AirPassengers), level = 90, h = 12 * 2),
  fillOpacity = 0.7
  ) %>%
  hc_xAxis(min = datetime_to_timestamp(as.Date("1955-01-01"))) %>%
  hc_add_theme(hc_theme_index)

# example 3
data(GNI2014, package = "treemap")
GNI2014 <- select(GNI2014, -population, -continent)
p3 <- hcmap(
  "custom/world-robinson-lowres",
  data = GNI2014,
  name = "GNI",
  value = "GNI",
  joinBy = c("iso-a3", "iso3"),
  nullColor = "#932667"
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    type = "logarithmic"
    ) %>%
  hc_legend(enabled = FALSE) %>%
  hc_mapNavigation(enabled = FALSE) 

# example 4
p4 <- hcboxplot(
  iris$Sepal.Length,
  var = iris$Species,
  name = "Sepal Length",
  color = "red"
  ) %>%
  hc_xAxis(showLastLabel = TRUE, showFirstLabel = TRUE) %>% 
  hc_add_theme(hc_theme_index)

# example 5
library(igraph)

set.seed(12313)
N <- 24
net <- sample_pa(N)
wc <- cluster_walktrap(net)
V(net)$label <- 1:N
V(net)$name <- 1:N
V(net)$page_rank <- round(page.rank(net)$vector, 2)
V(net)$betweenness <- round(betweenness(net), 2)
V(net)$degree <- degree(net)
V(net)$size <- V(net)$degree + 1
V(net)$comm <- membership(wc)
V(net)$color <- colorize(membership(wc), viridisLite::magma(length(wc)))
p5 <- hchart(net, layout = layout_with_fr, maxSize = 13)
  
# example 6
p6 <- hciconarray(
  c("bicycle", "taxi", "subway"),
  c(17, 12, 6),
  rows = 4,
  icons = c("bicycle", "taxi", "subway"),
  showInLegend = TRUE
  ) %>%
  hc_colors(c("darkgreen", "#CCCC00", "#808183"))
  
# example 7
p7 <- highchart() %>%
  hc_chart(type = "area") %>% 
  hc_add_series(density(rnorm(10000000)), name = "Normal Distribution") %>%
  hc_add_series(density(rgamma(10000000, 5, 0.8)), name = "Gamma(5. 0.8) Distribution") %>%
  # hc_add_series(density(rgamma(10000000, 3, 0.8)), name = "Gamma(3. 0.8) Distribution") %>%
  hc_plotOptions(series = list(fillOpacity = 0.5)) %>%
  hc_xAxis(min = -5, max = 12) %>% 
  hc_add_theme(hc_theme_index)

# example 8
brks <- seq(-3, 3, length.out = 40)
grid <- expand.grid(brks, brks)
m <- as.data.frame(grid) %>%
  mutate(
    value =
      mvtnorm::dmvnorm(grid, mean = c(1, 1), sigma = matrix(c(1, .2, .2, 1), nrow = 2)) +
      mvtnorm::dmvnorm(grid, mean = c(-1,-1), sigma = matrix(c(1,-.8,-.8, 1), nrow = 2)) +
      mvtnorm::dmvnorm(grid, mean = c(0, 0), sigma = matrix(c(1.5, 0, 0, 1.5), nrow = 2))
    ) %>%
  spread(Var2, value) %>%
  select(-Var1) %>%
  as.matrix()
  
colnames(m) <- rownames(m) <-  NULL
ncols <- 10
cols <- c(rep("white", 2), rev(viridisLite::inferno(ncols - 2, begin = 0)))
cols <- hex_to_rgba(cols, alpha = 1:ncols / ncols)
colssotps <- list_parse2(
  data.frame(
    q = seq(0, ncols - 1) / (ncols - 1),
    c = cols
    )
  )
  
p8 <- hchart(m) %>%
  hc_add_theme(hc_theme_null()) %>%
  hc_legend(enabled = FALSE) %>%
  hc_colorAxis(stops = colssotps)
  

# example 8
library(rwars)
swmovies <- get_all_films()
  
swdata <- map_df(swmovies$results, function(x) {
  data_frame(
  movie = x$title,
  species = length(x$species),
  planets = length(x$planets),
  characters = length(x$characters),
  vehicles = length(x$vehicles),
  release = x$release_date
  )
  })
  
swdata <- gather(swdata, key, number,-movie,-release) %>% 
  arrange(release)

p9 <- hchart(
  swdata,
  "line",
  hcaes(x = movie, y = number, group = key),
  color = c("#e5b13a", "#4bd5ee", "#4AA942", "#FAFAFA")
  ) %>%
  hc_xAxis(visible = FALSE) %>%
  hc_title(
    text = "Diversity in <span style=\"color:#e5b13a\"> STAR WARS</span> movies",
    style = list(fontSize = "13px"),
    useHTML = TRUE
    ) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_credits(
    enabled = TRUE,
    text = "Source: SWAPI via rwars package",
    href = "https://swapi.co/"
    ) %>%
  hc_add_theme(
    hc_theme_flatdark(
      chart = list(
        backgroundColor = "transparent",
        divBackgroundImage = "http://www.wired.com/images_blogs/underwire/2013/02/xwing-bg.gif"
        )
      )
    )

# example 10
p10 <- hchart(rgamma(10000, shape = 2, scale = 3)) %>% 
  hc_add_theme(hc_theme_smpl()) %>% 
  hc_add_theme(hc_theme_index)

plots <- list(
  p1, p2, 
  p3, p9, 
  p4, p7, 
  p5, p10
  #, p8, p6
  )

plots <- map(plots, hc_size, height = 300)

divplots <- map(plots, tags$div, class = "col-sm-6")

divplots <- htmltools::tagList(tags$div(class = "row", style = "padding-right: 10px", divplots))

# htmltools::browsable(divplots)

divplots
  
```


Highcharter is a [R](https://cran.r-project.org/) wrapper for 
**[Highcharts](https://www.highcharts.com/)**  javascript libray and its modules.
Highcharts is very mature and flexible javascript charting library and 
it has a great and powerful API^[See http://www.highcharts.com/demo].

The main features of this package are:

* Various chart type: scatters, bubble, line, 
time series, heatmaps, treemap, bar charts, networks.
* Chart various R object with one function. With hchart(x) you can 
chart: data.frames, numeric, histogram, character, density, factors, ts,
 mts, xts, stl, ohlc, acf, forecast, mforecast, ets, igraph, dist,
  dendrogram, phylo, survfit classes.
* Support Highstock charts. You can create a candlestick charts in 2 lines 
of code. Support xts objects from the quantmod package.
* Support Highmaps charts. It's easy to create choropleths or add 
information in geojson format.
* Themes: you configurate your chart in multiples ways. There are
 implemented themes like economist, financial times, google, 538 among 
 others.
* A lot of Plugins: motion, drag points, fontawesome, url-pattern, annotations.


## Highcharts: Hello World Example 

This is a simple example using `hchart` function.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
options(highcharter.theme = hc_theme_smpl())
```

```{r}
library(highcharter)
data(diamonds, mpg, package = "ggplot2")

hchart(mpg, "scatter", hcaes(x = displ, y = hwy, group = class))
```

Among its features highcharter can chart various objects depending of
its class with the generic^[I want to say *magic*]  `hchart` function.

```{r}
x <- c(rnorm(1000), rnorm(500, 5))

hchart(x, name = "data") 
```

One of the nicest class which `hchart` can plot is the `forecast`
class from the forecast package.

```{r}
library(forecast)

airforecast <- forecast(auto.arima(AirPassengers), level = 95)

hchart(airforecast)
```

## Highstock

With highcharter you can use the highstock library which 
include sophisticated navigation options like a small navigator 
series, preset date ranges, date picker, scrolling and panning.
With highcarter it's easy make candlesticks or ohlc charts using
time series data. For example data from [quantmod](http://www.quantmod.com/)
package.

```{r}
library(quantmod)

x <- getSymbols("GOOG", auto.assign = FALSE)
y <- getSymbols("AMZN", auto.assign = FALSE)

highchart(type = "stock") %>% 
   hc_add_series(x) %>% 
   hc_add_series(y, type = "ohlc")
```

## Highmaps

You can chart maps and choropleth using the highmaps module., build interactive 
maps to display data linked to geographic objects. 

```{r}
data(GNI2014, package = "treemap")

hcmap(
  "custom/world-robinson-lowres",data = GNI2014,
  name = "GNI",
  value = "GNI",
  joinBy = c("iso-a3", "iso3")
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    type = "logarithmic"
    ) 
```

