---
title: "Demostration of New Function `hctreemap2`"
author: "Alex Hayes"
date: "June 18, 2017"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(highcharter)
library(treemap)
library(RColorBrewer)
data(GNI2014)
```

This pull request is to address the following issues in the Highcharter function `hctreemap`:

* hctreemap() fails to render with cellnames repeated across levels #310
* bug in treemap when index variables have same values #32
* Does not work correctly for 3 level Treemaps #117
* hc_add_series_treemap - naming of the color value variable #98
* review/rework treemap fns #110

# New Dependencies

* `dplyr` >= 0.5.0.9005
* `rlang` >= 0.1.1

Both of these are included in the latest release of the `tidyverse` to CRAN. I got a R CMD Check Note for using NSE, which I resolved by adding

`if (getRversion() >= "2.15.1")  utils::globalVariables(c(".", "colorValue", "level", "name", "parent"))`

to the `highcharter-package.R` file. This is new to me, so I figured if you have a preference for how to sort this out you'll know how to change this better than I do.

# Interface Change and Old Interface Deprecation

This pull request includes the function `hctreemap2` which has the following interface

`hctreemap2(data, group_vars, size_var, color_var = NULL, ...)`

Note that this function accepts a dataframe rather than a `treemap::treemap` object. `hctreemap` remains unaltered, albeit with a deprecation warning.

The old interface looks like this

```{r, fig.keep = "none", warn = FALSE}
treemap(GNI2014,
        index = c("continent", "iso3"),
        vSize = "population",
        vColor = "GNI",
        type = "value",
        draw = FALSE) %>% 
  hctreemap(allowDrillToNode = TRUE, layoutAlgorithm = "squarified") %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            Pop: {point.value:,.0f}<br>
                            GNI: {point.valuecolor:,.0f}")
```

and the new interface looks very similar

```{r}
hctreemap2(data = GNI2014,
           group_vars = c("continent", "iso3"),
           size_var = "population",
           color_var = "GNI",
           layoutAlgorithm = "squarified",
           levelIsConstant = FALSE,
           levels = list(
             list(level = 1, dataLabels = list(enabled = TRUE)),
             list(level = 2, dataLabels = list(enabled = FALSE)),
             list(level = 3, dataLabels = list(enabled = FALSE))
           )) %>% 
  hc_colorAxis(minColor = brewer.pal(7, "Greens")[1],
               maxColor = brewer.pal(7, "Greens")[7]) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            Pop: {point.value:,.0f}<br>
                            GNI: {point.colorValue:,.0f}")
```

Likely the biggest difference for users will be that they'll need to specify the color palette themselves via `hc_colorAxis` rather than being able to make use of the `palette` argument in `treemap::treemap`. By default, `hctreemap2` enables a color axis with minimum and maximum values determined by at the lowest depth in the treemap, in keeping with `treemap::treemap`. I've included the above as an example in the function documentation, so hopefully people will get the hint about how to use `RColorBrewer` to make their lives better.

If the user doesn't specify a variable for the color mapping, the variable for the size mapping is used by default. Additionally, `allowDrillToNode` defaults to `TRUE`.

We can make a rather boring three level treemap to demonstrate that three level treemaps work

```{r}
data.frame(index1 = sample(LETTERS[1:3], 500, replace = T),
           index2 = sample(LETTERS[4:6], 500, replace = T),
           index3 = sample(LETTERS[7:9], 500, replace = T),
           value = rpois(500, 5)) %>%
  hctreemap2(
    group_vars = c("index1", "index2", "index3"),
    size_var = "value"
  )
```

# Non-Unique Cells Names Throw An Error

```{r, error = TRUE}
set.seed(27)

data.frame(
  index1 = sample(LETTERS[1:6], 500, replace = T),
  index2 = sample(LETTERS[1:6], 500, replace = T),
  value = abs(rnorm(500))) %>% 
  hctreemap2(c("index1", "index2"), "value")

```

The error checking also catches missing data:

```{r, error = TRUE}
data.frame(
  index1 = c(1, NA),
  index2 = c(NA, 2),
  value = abs(rnorm(500))) %>% 
  hctreemap2(c("index1", "index2"), "value")

```

This forces users to recode their data before continuing and should allow arbitrary depth treemaps. Lastly, a single level treemap just as another example

```{r}
hctreemap2(data = GNI2014,
           group_vars = "continent",
           size_var = "population") %>% 
  hc_colorAxis(minColor = brewer.pal(7, "Greens")[1],
               maxColor = brewer.pal(7, "Greens")[7]) %>% 
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            Pop: {point.value:,.0f}<br>
                            GNI: {point.colorValue:,.0f}")
```

