---
title: "Charting Data Frames"
author: "Joshua Kunst"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating Highcharts Demos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

We chart data. Data can come in different ways: numeric or character vectors,
as time series objects, etc. but the most common object with data is a data 
frame. So, why can chart this type of object in __highcharter__?

Highcharter have two main functions to chart data.

1. `hchart`: A generic function which take an object like vector, time series,
data frames, likert object and return a `highchart` object (chart)
2. `hc_add_series`: Another generic function which add data to a existing
`highchart` object depending the type (class) of the data.


This 3 functions are inspired in __ggplot2__ package. So:

- `hchart` works like ggplot2's `qplot`.
- `hc_add_series` works like ggplot2's `geom_`s.
- `hcaes` works like ggplot2's `aes`.

The main differences with ggplot2 are here we need explicit the data and the
aesthetics in every highchart functions. Lets see example to be more clear.

```{r, message=FALSE}
library(highcharter)
options(highcharter.theme = hc_theme_smpl(), highcharter.debug = TRUE) # we'll use a custom theme
```

```{r}
data("mpg", package = "ggplot2")
head(mpg)
```

```{r}
hchart(mpg, "point", hcaes(x = displ, y = cty))
```

The previous code is same as:

```{r}
highchart() %>% 
  hc_add_series(mpg, "point", hcaes(x = displ, y = cty))
```

