---
title: "Charting Maps"
author: "Joshua Kunst"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating Highcharts Demos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(highcharter)
set.seed(123)
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
options(highcharter.download_map_data = TRUE,
        highcharter.theme = hc_theme_smpl())
```

## Basics

The easiest way to chart a map with highcharter is select a map (a url) 
from the highmaps collection https://code.highcharts.com/mapdata/. Then use
the `hcmap` function.

```{r, warning=FALSE, message=FALSE}
hcmap("countries/nz/nz-all")
hcmap("custom/usa-and-canada")
```

__Note__: _The copyright information is added to the chart credits by default, 
but please be aware that you will have to display this information somewhere 
else if you choose to disable chart credits. Copyright information for each map
can be found as properties in the GeoJSON and Javascript files_.

## Choropleths

What about add data to get a choropleth? Every map downloaded from the 
highcharts maps collection have keys to join data. There are 2 functions
to help to know what are the regions coded to know how to join the map
and data:

- `download_map_data`: Download the geojson data from the highcharts collection.
- `get_data_from_map`: Get the properties  for each region in the map, as the keys
from the map data.

```{r}
require(dplyr)

mapdata <- get_data_from_map(download_map_data("countries/us/us-all"))
glimpse(mapdata)

data_fake <- mapdata %>% 
  select(code = `hc-a2`) %>% 
  mutate(value = abs(rt(nrow(.), df = 10)))

glimpse(data_fake)
```

If we compare this 2 data frames the `hc-key` is same code that
`code`. So we'll use these columns as keys:

```{r}
hcmap("countries/us/us-all", data = data_fake, value = "value",
      joinBy = c("hc-a2", "code"), name = "Unemployment",
      dataLabels = list(enabled = TRUE, format = '{point.code}'),
      borderColor = "#FAFAFA", borderWidth = 0.1) %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_add_theme(hc_theme_db())
```

## Adding More Data

```{r}
cities <- data_frame(
  name = c("London", "Birmingham", "Glasgow", "Liverpool"),
  lat = c(51.507222, 52.483056,  55.858, 53.4),
  lon = c(-0.1275, -1.893611, -4.259, -3),
  z = c(1, 2, 3, 2)
)

glimpse(cities)

hcmap("countries/gb/gb-all", showInLegend = FALSE) %>% 
  hc_add_series(data = cities, type = "mapbubble", name = "Cities", maxSize = '10%') %>% 
  hc_mapNavigation(enabled = TRUE) 
```

## Advanced Maps & `geojsonio` Package

Highcharts support `geo_json` classes from the `geojsonio` package. 

A good resource for geojson countries is https://github.com/johan/world.geo.json.

```{r}
# library(geojsonio)

getContent <- function(url) {
  library(httr)
  content(GET(url))
}

world <- getContent("https://raw.githubusercontent.com/johan/world.geo.json/master/countries.geo.json")
# is text
world <- jsonlite::fromJSON(world, simplifyVector = FALSE)

# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_corrientes_maritimas
marine <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_corrientes_maritimas&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# marine <- geojsonio::as.json(marine)


# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_limites_placas
plates <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_limites_placas&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# plates <- geojsonio::as.json(plates)

# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_volcanes
volcano <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_volcanes&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# volcano <- geojsonio::as.json(volcano)

highchart(type = "map") %>%
  hc_title(text = "Marine Currents, Plates & Volcanos") %>%
  hc_add_series(mapData = world, showInLegend = FALSE) %>%
  hc_add_series(data = marine, type = "mapline", geojson = TRUE,
                name = "Marine currents", tooltip = list(pointFormat = "{point.properties.NOMBRE}")) %>%
  hc_add_series(data = plates, type = "mapline", lineWidth = 2, zIndex = 0, geojson = TRUE,
                name = "Plates", tooltip = list(pointFormat = "{point.properties.TIPO}")) %>%
  hc_add_series(data = volcano, type = "mappoint", color = hex_to_rgba("darkred", 0.2), geojson = TRUE,
                name = "Volcanos", tooltip = list(pointFormat = "{point.properties.NOMBRE}"))
```

```{r}
# library(geojsonio)
# 
# ausgeojson <- getContent("https://raw.githubusercontent.com/johan/world.geo.json/master/countries/AUS.geo.json")
# ausgeojson <- jsonlite::fromJSON(ausgeojson, simplifyVector = FALSE)
# ausgeojson <- geojsonio::as.json(ausgeojson)
# 
# # http://openflights.org/data.html
# airports <- read.csv("https://commondatastorage.googleapis.com/ckannet-storage/2012-07-09T214020/global_airports.csv")
# airports <- filter(airports, country == "Australia", name != "Roma Street Railway Station")
# 
# airp_geojson <- geojson_json(airports, lat = "latitude", lon = "longitude")
# 
# highchart(type = "map") %>% 
#   hc_add_series(mapData = ausgeojson, showInLegend = FALSE, nullColor = "#A9CF54") %>%
#   hc_add_series(data = airp_geojson, type = "mappoint", dataLabels = list(enabled = FALSE),
#                 name = "Airports", color = 'rgba(250, 250, 250, 0.7)',
#                 tooltip = list(pointFormat = "{point.name}")) %>% 
#   hc_add_theme(hc_theme_db())
```


