---
title: "Charting Maps"
author: "Joshua Kunst"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating Highcharts Demos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(highcharter)
options(highcharter.theme = hc_theme_smpl(),
        highcharter.download_map_data = TRUE)
```

## Basics

The easiest way to chart a map with highcharter is select a map (a url) 
from the highmaps list https://code.highcharts.com/mapdata/. Then use
the `hcmap` function.

```{r, warning=FALSE, message=FALSE}
hcmap("countries/nz/nz-all")
hcmap("custom/usa-and-canada")
```

__Note__: The copyright information is added to the chart credits by default, 
but please be aware that you will have to display this information somewhere 
else if you choose to disable chart credits. Copyright information for each map
can be found as properties in the GeoJSON and Javascript files.

What about add data to get a choropleth? Every map downloaded from the 
highcharts maps collection have key to join data.
