---
title: "Charting Maps"
author: "Joshua Kunst"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Charting Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, warning = FALSE, message = FALSE, echo = FALSE}
library(highcharter)
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
options(highcharter.theme = hc_theme_smpl())
```

## Basics

The easiest way to chart a map with highcharter is using `hcmap` function.
Select a map (a url) from the highmaps collection 
https://code.highcharts.com/mapdata/.
and use the url as a map in `hcmap` function. This will download the map
and create a \code{highchart} object using the info as a `mapData` argument.


```{r, warning=FALSE, message=FALSE}
hcmap("countries/nz/nz-all")
hcmap("custom/usa-and-canada", showInLegend = FALSE)
hcmap("countries/us/us-ca-all") %>%
  hc_title(text = "California")
```

__Note__: _The copyright information is added to the chart credits by default, 
but please be aware that you will have to display this information somewhere 
else if you choose to disable chart credits. Copyright information for each map
can be found as properties in the GeoJSON and Javascript files_.

## Choropleths

What about add data to get a choropleth? Every map downloaded from the 
highcharts maps collection have keys to join data. There are 2 functions
to help to know what are the regions coded to know how to join the map
and data:

- `download_map_data`: Download the geojson data from the highcharts collection.
- `get_data_from_map`: Get the properties  for each region in the map, as 
the keys from the map data.

```{r}
require(dplyr)

mapdata <- get_data_from_map(download_map_data("countries/us/us-all"))
glimpse(mapdata)

set.seed(1234)

data_fake <- mapdata %>% 
  select(code = `hc-a2`) %>% 
  mutate(value = 1e5 * abs(rt(nrow(.), df = 10)))

glimpse(data_fake)
```

If we compare this 2 data frames the `hc-key` is same code that
`code`. So we'll use these columns as keys:

```{r}
hcmap("countries/us/us-all", data = data_fake, value = "value",
      joinBy = c("hc-a2", "code"), name = "Fake data",
      dataLabels = list(enabled = TRUE, format = "{point.name}"),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 2, valuePrefix = "$", valueSuffix = "USD")) 
```

## Adding More Data

With highcharter is possible add data as points or bubbles. For this it is 
necessary a data frame with `lat`, `lon` columns, and `name`, `z`  are
optional:

```{r}
data("quakes")

quakes <- quakes %>% 
  rename(lon = long) %>% 
  mutate(z = mag,
         color = colorize(depth)) %>% 
  filter(z > 5)

glimpse(quakes)

hcmap("countries/fj/fj-all", name = "Fiji") %>% 
  hc_add_series(data = quakes, type = "mapbubble",
                name = "Quakes", maxSize = "10") %>% 
  hc_title(text = "Locations of Earthquakes off Fiji") %>% 
  hc_subtitle(text = "Locations of seismic events of MB > 5.0. The events 
              occurred in a cube near Fiji since 1964")
```

## Advanced Maps

Sometime you will need to use other source of maps. You can load geojson as a
list. For example a good resource for geojson countries is 
https://github.com/johan/world.geo.json. Just ensure use `geojson = TRUE` to
internally transform the list in a format usable for highcharts.

Let's download some geojson file and make a map.

```{r}
getContent <- function(url) {
  library(httr)
  content(GET(url))
}

world <- getContent("https://raw.githubusercontent.com/johan/world.geo.json/master/countries.geo.json")
# is text
world <- jsonlite::fromJSON(world, simplifyVector = FALSE)

# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_corrientes_maritimas
marine <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_corrientes_maritimas&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# marine <- geojsonio::as.json(marine)


# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_limites_placas
plates <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_limites_placas&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# plates <- geojsonio::as.json(plates)

# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_volcanes
volcano <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_volcanes&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# volcano <- geojsonio::as.json(volcano)

```

The data is ready. Remember you can keep using the rest of the API to 
customize your map.

```{r}
highchart(type = "map") %>%
  hc_chart(backgroundColor = "#161C20") %>% 
  hc_add_series(mapData = world, showInLegend = FALSE, nullColor = "#424242",
                borderWidth = 0) %>%
  hc_add_series(data = marine, type = "mapline", geojson = TRUE,
                color = "#2980b9", name = "Marine currents",
                tooltip = list(pointFormat = "{point.properties.NOMBRE}")) %>%
  hc_add_series(data = plates, type = "mapline", lineWidth = 2, zIndex = -1,
                geojson = TRUE,
                color = "#d35400", name = "Plates",
                tooltip = list(pointFormat = "{point.properties.TIPO}")) %>%
  hc_add_series(data = volcano, type = "mappoint",
                color = hex_to_rgba("#f1c40f", 0.4),
                geojson = TRUE, name = "Volcanos",
                tooltip = list(pointFormat = "{point.properties.NOMBRE}"),
                marker = list(lineWidth = 0, radius = 2))
```

## `geojsonio` Package

Highcharts support `geo_json` classes from the `geojsonio` package. So you 
can use `hc_add_series` as usual without use `geojson = TRUE` 
parameter/argument.


```{r, echo=TRUE, eval=FALSE}
library(geojsonio)

ausgeojson <- getContent("https://raw.githubusercontent.com/johan/world.geo.json/master/countries/AUS.geo.json")
ausgeojson <- jsonlite::fromJSON(ausgeojson, simplifyVector = FALSE)
ausgeojson <- geojsonio::as.json(ausgeojson)
class(ausgeojson)

# http://openflights.org/data.html
airports <- read.csv("https://commondatastorage.googleapis.com/ckannet-storage/2012-07-09T214020/global_airports.csv")
airports <- filter(airports,
                   country == "Australia", 
                   name != "Roma Street Railway Station")

airp_geojson <- geojson_json(airports, lat = "latitude", lon = "longitude")
class(airp_geojson)

highchart(type = "map") %>%
  hc_add_series(mapData = ausgeojson, showInLegend = FALSE) %>%
  hc_add_series(data = airp_geojson, type = "mappoint",
                dataLabels = list(enabled = FALSE),
                name = "Airports", tooltip = list(pointFormat = "{point.name}")) 
```

```{r, eval=FALSE, include=FALSE}
library(highcharter)
library(dplyr)
library(purrr)

set.seed(1234)

n <- 20
z <-  sample(1:n)
sequences <- map2(1:n, z, function(x, y){ ifelse(x == 1:n, y, 0) })

df <- data_frame(
  lat = runif(n, -180, 180),
  lon = runif(n, -180, 180),
  z = z,
  color = colorize(z),
  sequence = sequences
  )

hcmap() %>% 
  hc_add_series(data = df, type = "mapbubble",
                minSize = 0, maxSize = 30) %>% 
  hc_motion(enabled = TRUE, series = 1, labels = 1:n,
            loop = TRUE, autoPlay = TRUE, 
            updateInterval = 1000, magnet = list(step =  1)) %>% 
  hc_plotOptions(series = list(showInLegend = FALSE))
```

