---
title: Drilldown
author: Joshua Kunst
date: "`r Sys.Date()`"
description: >
  Drilldown is the concept of inspecting increasingly high resolution data
  through clicking on chart items like columns, points or pie slices. 
  Let's see some _How tos_ use this feature.
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "arrow-down"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

Drilldown is the concept of inspecting increasingly high resolution data
through clicking on chart items like columns, points or pie slices.

## Exmaple I: Gapminder data

```{r, include=FALSE}
library(highcharter)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, out.width="100%")
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
options(download.file.method = "libcurl")
```


```{r}
library(tidyverse)
data(gapminder, package = "gapminder")

gapminder2007 <- gapminder |> 
  filter(year == max(year)) |> 
  select(-year) |> 
  mutate(pop = pop/1e6) |> 
  arrange(desc(pop))

gapminder_column <- gapminder2007 |>
  group_by(continent) |> 
  summarise(
    lifeExp = weighted.mean(lifeExp, pop),
    gdpPercap = weighted.mean(gdpPercap, pop),
    pop = sum(pop)
  ) |> 
  mutate_if(is.numeric, round) |> 
  arrange(desc(pop)) |> 
  mutate(continent = fct_inorder(continent))

gapminder_column

gapminder_drilldown <- gapminder2007 |> 
  group_nest(continent) |> 
  mutate(
    id = continent,
    type = "column",
    # in the drilldown we'll give the mapping via creating the columns
    data = map(data, mutate, name = country, y  = pop),
    data = map(data, list_parse)
  )

gapminder_drilldown
```

The data is ready. Now, in this example due the continents and countries have
the sames values (pop, lifeExp, ...) we can use the same `pointFormat` for 
the tooltips:


```{r}
x <- c("Population (MM)", "Life expectancy at birth", "GDP per capita (US$)")
y <- c("{point.pop}", "{point.lifeExp}", "$ {point.gdpPercap}")

tt <- tooltip_table(x, y)

hchart(
  gapminder_column,
  "column",
  hcaes(x = continent, y = pop, name = continent, drilldown = continent),
  name = "Population",
  colorByPoint = TRUE
) |> 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series = list_parse(gapminder_drilldown)
  ) |> 
  hc_tooltip(
    pointFormat = tt, # "{point.name} {point.pop}"
    useHTML = TRUE,
    valueDecimals = 0
  ) |> 
  hc_yAxis(
    title = list(text = "Population in millions (log scale)"),
    type = "logarithmic",
    minorTickInterval = 'auto'
  ) |> 
  hc_xAxis(
    title = ""
  )
```

## Exmaple II: Pokémon data

Copy & pasting same code:

```{r}
pkmn_min <- pokemon |> 
  count(type_1, color = type_1_color) |> 
  mutate(type_1 = fct_reorder(type_1, .x = n)) |> 
  arrange(desc(type_1))

pkmn_ddn <- pokemon |> 
  count(type_1, type_2, color = type_mix_color) |> 
  arrange(type_1, desc(n)) |> 
  mutate(type_2 = ifelse(is.na(type_2), str_c("only ", type_1), type_2)) |> 
  group_nest(type_1) |> 
  mutate(
    id = type_1,
    type = "column",
    # in the drilldown we'll give the mapping via creating the columns
    data = map(data, mutate, name = type_2, y  = n),
    data = map(data, list_parse)
  )
  
hchart(
  pkmn_min, 
  type = "column",
  hcaes(x = type_1, y = n, color = color, drilldown = type_1),
  name = "Pokémons"
  ) |> 
  hc_drilldown(
    activeAxisLabelStyle = list(textDecoration = "none"),
    allowPointDrilldown = TRUE,
    series = list_parse(pkmn_ddn)
  ) |> 
  hc_yAxis(
    title = list(text = ""),
    endOnTick = FALSE,
    opposite = TRUE
    ) |>
  hc_xAxis(
    title = list(text = ""),
    endOnTick = FALSE,
    gridLineWidth = 0,
    tickWidth = 0
    ) |> 
  hc_chart(
    style = list(fontFamily = "Gloria Hallelujah")
  ) 
```

