---
title: Fontawesome integration
author: Joshua Kunst
date: "`r Sys.Date()`"
description: >
  Take a look on how you can add incons to the text or even use the icons
  as marker points.
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "font-awesome"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
library(highcharter)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, out.width="100%")
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
options(download.file.method = "libcurl")
```

The easiest way to use fontawesome icons with highcharter is using the
the package with the same name by Richard Iannone https://github.com/rstudio/fontawesome
because you can turn the icons into svg text or png files so you can use them in 
html tags or transform to data uri.

```{r}
library(rsvg)
library(fontawesome)
library(highcharter)
library(stringr)

df <- data.frame(
  a = round(rnorm(10), 2),
  b = round(rnorm(10), 2)
)

fa_to_png_to_datauri <- function(name, ...) {
  
  tmpfl <- tempfile(fileext = ".png")
  
  fontawesome::fa_png(name, file = tmpfl, ...)
  
  knitr::image_uri(tmpfl)
  
}

# specify colors tu resue in the series/tooltips
rcol <- "#4C83B6"
pcol <- "#3CAB48"

rproj <- fa_to_png_to_datauri(name = "r-project", width = 22, fill = rcol)
pthon <- fa_to_png_to_datauri(name = "python",    width = 22, fill = pcol)

highchart() %>% 
  hc_title(
    text = str_c("This is a svg ", fa("rocket", fill = "#CACACA"), " icon"),
    useHTML = TRUE
  ) %>% 
  hc_add_series(
    df,
    "scatter",
    hcaes(a, b),
    name = "R icons",
    color = rcol,
    marker = list(symbol = str_glue("url({data_uri})", data_uri = rproj)),
    icon = rproj
  ) %>% 
  hc_add_series(
    df,
    "scatter",
    hcaes(b, a),
    name = "Python icons",
    color = pcol,
    marker = list(symbol = str_glue("url({data_uri})", data_uri = pthon)),
    icon = pthon
  ) %>% 
  hc_tooltip(
    pointFormat = str_c(
      "<b>",
      "<img style='vertical-align:middle' height='15' src='{series.options.icon}'/> ",
      "[{point.x}, {point.y}]",
      "</b>"
    ),
    useHTML = TRUE
  )
```

Another example inspired/copied from https://github.com/hrbrmstr/waffle:

```{r}
library(dplyr) # to wokr with list columns
library(purrr) # to wokr with list columns

df2 <- tibble(
  type = c("fruit", "samminch", "pizza"),
  amount = c(46, 54, 80),
  faico = c("apple-alt", "bread-slice", "pizza-slice"),
  col = c("#d35400", "#907E4D", "#F89101")
)

df2

df2 <- df2 %>% 
  mutate(
    uri = map2_chr(faico, col, ~fa_to_png_to_datauri(.x, fill = .y)),
    marker = map(uri, ~ list(symbol = str_glue("url({data_uri})", data_uri = .x)))
  )

hchart(
  df2,
  "item",
  hcaes(name = type, y = amount),
  name = "What I eat",
  showInLegend = TRUE
  ) %>% 
  hc_plotOptions(
    # avoid hide series due bug
    series = list(point = list(events = list(legendItemClick = JS("function(e) {e.preventDefault() }"))))
  ) %>% 
  hc_legend(
    labelFormat =  '{name} <span style="opacity: 0.4">{y}</span>'
  ) %>% 
  hc_colors(pull(df2, col))
```

More details in item chart in this link 
https://www.highcharts.com/docs/chart-and-series-types/item-chart.

