---
title: Highcharts API
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  Highcharts have a rich API which allows you to have control of the entire chart, 
  from title, subtitle to axis ticks, labels, annotations. We'll review the
  main functions with simple examples.
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Highcharts API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}    
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "cogs"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, out.width="100%", eval = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
```

Highcharts have a rich API which allows you to have control of the entire chart, 
from title, subtitle to axis ticks, labels, annotations. We'll review the
main functions with simple examples.

## Before to start

- There's not default arguments. All arguments need to be named.
- You can see more examples for arguments in https://api.highcharts.com/highcharts/.

If this is clear, we can continue.

Now, let's create a simple chart:

```{r}
library(highcharter)

data("citytemp")

hc <- highchart() |> 
  hc_xAxis(categories = citytemp$month) |> 
  hc_add_series(
    name = "Tokyo", data = citytemp$tokyo
    ) |> 
  hc_add_series(
    name = "London", data = citytemp$london
    ) |> 
  hc_add_series(
    name = "Other city",
    data = (citytemp$tokyo + citytemp$london)/2
    )

hc
```

## Chart

With `hc_chart` you can define general chart options.

```{r}
hc |> 
  hc_chart(
    borderColor = '#EBBA95',
    borderRadius = 10,
    borderWidth = 2,
    backgroundColor = list(
      linearGradient = c(0, 0, 500, 500),
      stops = list(
        list(0, 'rgb(255, 255, 255)'),
        list(1, 'rgb(200, 200, 255)')
        )
      )
    )
```

Now change type to column and add 3d effect.

```{r}
hc <- hc |> 
  hc_chart(
    type = "column",
    options3d = list(
      enabled = TRUE, 
      beta = 15,
      alpha = 15
      )
    )
hc

# back to the line!
hc <- hc_chart(hc, type = "line", options3d = list(enabled = FALSE))
```

## Title, subtitle, caption and credits

A good chart always have at least title, right? Then you can do it better adding relevant information
using a subtitle or caption, even link to the source of data:

```{r}
hc |> 
  hc_title(
    text = "This is the title of the chart"
    ) |> 
  hc_subtitle(
    text = "This is an intereseting subtitle to give
    context for the chart or some interesting fact"
    ) |> 
  hc_caption(
    text = "This is a long text to give some 
    subtle details of the data which can be relevant to the reader. 
    This is usually a long text that's why I'm trying to put a 
    <i>loooooong</i> text.", 
    useHTML = TRUE
    ) |> 
  hc_credits(
    text = "Chart created using R and highcharter",
    href = "http://jkunst.com/highcharter",
    enabled = TRUE
    )
```

## Axis

Usually is desirable get control or modify the behavior of the axis:

```{r}
hc |> 
  hc_xAxis(
    title = list(text = "Month in x Axis"),
    opposite = TRUE
    ) |> 
  hc_yAxis(
    title = list(text = "Temperature <b>in y Axis</b>", useHTML = TRUE),
    opposite = TRUE,
    minorTickInterval = "auto",
    minorGridLineDashStyle = "LongDashDotDot",
    showFirstLabel = FALSE,
    showLastLabel = FALSE
  )
```

A good feature is `plotLines` and `plotBand` which you can use in both axis. For example:

```{r}
hc |> 
  hc_xAxis(
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 4,
        # the zIndex is used to put the label text over the grid lines 
        zIndex = 1
        )
      )
    ) |> 
  hc_yAxis(
    plotBands = list(
      list(
        from = 20,
        to = 50,
        color = hex_to_rgba("red", 0.1),
        label = list(text = "This is a plotBand"),
        # the zIndex is used to put the label text over the grid lines 
        zIndex = 1
        )
      )
    ) 
```

## Legend & tooltip

```{r}
hc |>
  hc_legend(
    align = "left",
    verticalAlign = "top",
    layout = "vertical",
    x = 0, y = 100
    ) |>
  hc_tooltip(
    crosshairs = TRUE,
    backgroundColor = "#F0F0F0",
    shared = TRUE, 
    borderWidth = 5
    )
```


       


