---
title: Highcharter
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Highcharter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}    
---

<script>
  $(document).ready(function(){ 
    el = $(".page-header > h1")
    icon = "rocket"
    text = el.text()
    text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
    el.html(text_new) 
  }) ;
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt())
```

## <span class="fa fa-bar-chart"></span> Highcharts

let us start start with a simple example using `hchart` function.

```{r}
library(highcharter)

# install.packages("palmerpenguins")
data(penguins, package = "palmerpenguins") 

hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species)
)
```

Among its features {highcharter} can chart various objects depending of
its class with the generic `hchart` function.

```{r}
x <- c(rnorm(10000), rnorm(1000, 4, 0.5))

hchart(x, name = "data") 
```

One of the nicest class which `hchart` can plot is the `forecast`
class from the {forecast} package.


```{r}
library(forecast)

airforecast <- forecast(auto.arima(AirPassengers), level = 95)

hchart(airforecast)
```



