---
title: Highcharts API
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  Highcharts have a rich API which allows you to have control of the entire chart, 
  from title, subtitle to axis ticks, labels, annotations. We'll review the
  main functions with simple examples.
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "cogs"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
```

Highcharts have a rich API which allows you to have control of the entire chart, 
from title, subtitle to axis ticks, labels, annotations. We'll review the
main functions with simple examples.

## Before to start

- There's not default arguments. All arguments need to be named.
- You can see mor examples of _every_ arguments in https://api.highcharts.com/highcharts/

If this is clear, we can continue.

## Title, subtitle, caption and credits

Fist of all, let's create a simple chart:

```{r}
data(mpg, package = "ggplot2")
library(dplyr)
library(highcharter)

mpgc <- mpg %>% 
  count(year, class)

hc <- hchart(mpgc, "column", hcaes(class, n, group = year))
hc
```

A good chart always have at least title, right? Then you can do it better adding relevant information
using a subtitle or caption, even link to the source of data:

```{r}
hc %>% 
  hc_title(
    text = "This is the title of the chart"
    ) %>% 
  hc_subtitle(
    text = "This is an intereseting subtitle to give
    context for the chart or some interesting fact"
    ) %>% 
  hc_caption(
    text = "This is a long text to give some 
    subtle details of the data which can be relevant to the reader. 
    This is usually a long text that's why I'm trying to put a 
    <i>loooooong</i> text.", 
    useHTML = TRUE
    ) %>% 
  hc_credits(
    text = "Chart created using R and highcharter",
    href = "http://jkunst.com/highcharter",
    enabled = TRUE
    )
```

## Axis

Usually is desirable get control or modify the behavior of the axis:

```{r}
data("citytemp_long")

hc2 <- hchart(citytemp_long, "line", hcaes(month, temp, group = city))
hc2
```

```{r}
hc2 %>% 
  hc_xAxis(
    title = list(text = "Month in x Axis"),
    opposite = TRUE
    ) %>% 
  hc_yAxis(
    title = list(text = "Temperature <b>in y Axis</b>", useHTML = TRUE),
    opposite = TRUE,
    minorTickInterval = "auto",
    minorGridLineDashStyle = "LongDashDotDot",
    showFirstLabel = FALSE,
    showLastLabel = FALSE
  )
```

A good feature is `plotLines` and `plotBand` which you can use in both axis. For example:

```{r}
hc2 %>% 
  hc_xAxis(
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 4,
        # the zIndex is used to put the label text over the grid lines 
        zIndex = 1
        )
      )
    ) %>% 
  hc_yAxis(
    plotBands = list(
      list(
        from = 20,
        to = 50,
        color = hex_to_rgba("red", 0.1),
        label = list(text = "This is a plotBand"),
        # the zIndex is used to put the label text over the grid lines 
        zIndex = 1
        )
      )
    ) 
```

       


