---
title: Highcharter
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Highcharter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}    
---

<script>
  $(document).ready(function(){ 
    el = $(".page-header > h1")
    icon = "rocket"
    text = el.text()
    text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
    el.html(text_new) 
  }) ;
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt())
```

## <span class="fa fa-bar-chart"></span> Highcharts

let us start start with a simple example using `hchart` function.

```{r}
library(highcharter)

# install.packages("palmerpenguins")
data(penguins, package = "palmerpenguins") 

hchart(
  penguins,
  "scatter",
  hcaes(x = flipper_length_mm, y = bill_length_mm, group = species)
)
```

Among its features {highcharter} can chart various objects depending of
its class with the generic `hchart` function.

```{r}
x <- c(rnorm(10000), rnorm(1000, 4, 0.5))

hchart(x, name = "data") 
```

One of the nicest class which `hchart` can plot is the `forecast`
class from the {forecast} package.


```{r}
library(forecast)

airforecast <- forecast(auto.arima(AirPassengers), level = 95)

hchart(airforecast)
```

See more examples of `hchart` in `vignette("hchart")`.

## <span class="fa fa-line-chart"></span> Highstock

With {highcharter} you can use the highstock library which 
include sophisticated navigation options like:

- Small navigator series
- Preset date ranges
- Date picker
- Scrolling and panning.

It is easy make candlesticks or ohlc charts using time series data. For example, using data from 
[{quantmod}](http://www.quantmod.com/) package:

```{r}
library(quantmod)

x <- getSymbols("GOOG", auto.assign = FALSE)
y <- getSymbols("AMZN", auto.assign = FALSE)

highchart(type = "stock") |> 
  hc_add_series(x) |> 
  hc_add_series(y, type = "ohlc")
```

## <span class="fa fa-map-o"></span> Highmaps

We can chart maps elements and choropleth using the highmaps and
build interactive maps to display data linked to geographic objects.

<!-- ```{r} -->
<!-- data(GNI2014, package = "treemap") -->

<!-- hcmap( -->
<!--   "custom/world-robinson-lowres", -->
<!--   data = GNI2014, -->
<!--   name = "Gross national income per capita", -->
<!--   value = "GNI", -->
<!--   borderWidth = 0, -->
<!--   nullColor = "#d3d3d3", -->
<!--   joinBy = c("iso-a3", "iso3") -->
<!-- ) |> -->
<!--   hc_colorAxis( -->
<!--     stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)), -->
<!--     type = "logarithmic" -->
<!--   ) -->
<!-- ``` -->

## What now?

Since you know the basics now it could be interesting:

- Go motivate yourself with the `vignette("showcase")` and observe everything that can be
done with the {highcharter} package.
- Learn to configure graphics using the implemented API in `vignette("highcharts-api")`.
- See all chart you can make in `vignette("highcharts")`.

