---
title: Charts with highcharts
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  Highcharts is a SVG-based, multi-platform charting library. The highcharter 
  package bring all highchartsJS capabilities to your R console. So you can
  chart from simple charts like column, scatter to more complex charts like
  streamgraph, packedbubble, vector field among others.
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Charts with highcharts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "area-chart"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
library(highcharter)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
options(download.file.method = "libcurl")
```

Highcharts is a SVG-based, multi-platform charting library. The highcharter 
package bring all highchartsJS capabilities to your R console. So you can
chart from simple charts like column, scatter to more complex charts like
streamgraph, packed bubble, vector field among others.

## Basic charts

Let's see a preview of what highchartsJS (so highcharter) can chart. First of
all a simple data set:

```{r}
library(dplyr)
library(stringr)
library(purrr)

n <- 6

set.seed(123)

colors <- c("#d35400", "#2980b9", "#2ecc71", "#f1c40f", "#2c3e50", "#7f8c8d")
colors2 <- c("#000004", "#3B0F70", "#8C2981", "#DE4968", "#FE9F6D", "#FCFDBF")

df <- data.frame(x = seq_len(n) - 1) |> 
  mutate(
    y = 10 + x + 10 * sin(x - 1),
    z = 5 + (x*y) - median(x*y),
    e = 10 * abs(rnorm(length(x))) + 2,
    e = round(e, 1),
    low = y - e,
    high = y + e,
    value = round(y - 1),
    name = sample(fruit[str_length(fruit) <= 5], size = n),
    color = rep(colors, length.out = n)
  ) |> 
  mutate_if(is.numeric, round, 1) |> 
  select(-e)

df <- df |> 
  mutate(
    # label = name,
    from = name[c(1, 1, 1, 2, 3, 4)],
    to   = name[c(3, 4, 5, 3, 6, 6)],
    weight = c(1, 1, 1, 1, 2, 2)
  )
```

```{r echo=FALSE}
knitr::kable(df)
```


```{r, echo=FALSE}
create_hc <- function(t = "dumbbell") {
  
  dont_rm_high_and_low <- c(
    "arearange",
    "areasplinerange",
    "polarcolumnrange",
    "columnrange",
    "errorbar",
    "dumbbell"
    )
  
  if(!t %in% dont_rm_high_and_low) df <- df |> select(-low, -high)
  
  is_polar <- str_detect(t, "polar")
  type     <- str_remove(t, "polar")
  title    <- str_c(ifelse(is_polar, "polar ", ""), type)
  invt     <- ifelse(t %in% c("dumbbell", "organization"), TRUE, FALSE)  
  yvisible <- ifelse(t %in% c("streamgraph", "timeline"), FALSE, TRUE)
  xvisible <- ifelse(t %in% c(""), FALSE, TRUE)
  
  hcout <-  highchart() |>
    hc_title(
      text = title,
      style = list(fontSize = "15px")
      ) |> 
    hc_chart(
      type = type,
      polar = is_polar,
      inverted = invt
    ) |> 
    hc_xAxis(
      categories = df$name
      ) |> 
    hc_yAxis(
      visible = yvisible
    ) |> 
    hc_tooltip(
      outside = TRUE
    ) |> 
    hc_add_series(
      df,
      name = "Fruit Consumption",
      showInLegend = FALSE
      )
  
  hcout
  
}

hcs <- c(
  "line", "spline",  "area", "areaspline",
  "column", "columnpyramid", "bar", 
  "scatter", "bubble",
  "lollipop", 
  
  "waterfall" , "funnel", "pyramid",
  
  "pie" , "treemap", "packedbubble",

  "arearange", "areasplinerange", "columnrange", "errorbar", "dumbbell",
  "polygon", 
  
  "polarline", "polarcolumn", "polarcolumnrange",
  "streamgraph", "item", "wordcloud", "timeline",
  
  "sankey", "dependencywheel", "organization"
  )  |> 
  map(create_hc) 

hcs |> 
  map(hc_size, height = 300) %>% 
  {print(hw_grid(.)); .} |> 
  map(tags$div, class = "col-sm-4") |> 
  tags$div(class = "row")
```


<!-- ## xrange -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/xrange.R"))} -->
<!-- ``` -->

## vector

```{r code = readLines(here::here("dev/examples-charts/vector.R"))}
```

<!-- ## tilemap -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/tilemap.R"))} -->
<!-- ``` -->

<!-- ## packedbubble -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/packedbubble.R"))} -->
<!-- ``` -->

<!-- ## venn & euler -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/venn.R"))} -->
<!-- ``` -->

<!-- ## solidgauge -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/solidgauge.R"))} -->
<!-- ``` -->

<!-- ## bullet -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/bullet.R"))} -->
<!-- ``` -->

<!-- ## item -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/item.R"))} -->
<!-- ``` -->

<!-- ## sankey -->

<!-- ```{r code = readLines(here::here("dev/examples-charts/sankey.R"))} -->
<!-- ``` -->

