---
title: First steps on highcharter package
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  Start here if this is your first time with highcharter. You'll learn the main   
  functions to get a chart from a data frame and some basic examples.
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "rocket"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, warning = FALSE, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(), highcharter.debug = TRUE)
```

## Introduction

We chart data, and data can come in different ways: numeric or character vectors,
as time series objects, etc. but the most common object with data is a data 
frame. So, we'll show how  chart this type of object in __highcharter__.

Highcharter have two main functions to create a chart from data and another
to add data to an existing `highchart` object.

1. `hchart()`: A generic function which take an object (like vector, time series,
data frames, likert object, etc) and return a `highchart` object (chart)
2. `hc_add_series()`: A generic function which add data to a existing
`highchart` object depending the type (class) of the data.

There are a last function will be useful to chart data from data frame. The 
functions is `hcaes` which will define the aesthetic mappings. This 3 functions
are inspired in __ggplot2__ package. So:

- `hchart()` works like ggplot2's `qplot`.
- `hc_add_series()` works like ggplot2's `geom_`s.
- `hcaes()` works like ggplot2's `aes`.

The main differences with ggplot2 are here we need the data and the aesthetics
explicit in every highcharts functions. 

First, show some data to work with.

```{r}
data("mpg", "diamonds", "economics_long", package = "ggplot2")
head(mpg)
```

In general we'll use this structure to get a chart:

```
hchart(<data.frame>, <type_of_chart>, hcaes(<aesthetics>), ...)
```

- `<data.frame>` will be the data to chart.
- `<type_of_chart>` is a string to specify the type of chart. This value can 
be: line, spline, area, heatmap, treemap, etc.
- `<aesthetics>` is the mapping to use for plot.
- `...` are other parameters to configure the chart.

So, a basic example would be:

```{r}
hchart(mpg, "point", hcaes(x = displ, y = cty, group = year))
```

## Exercising the basics

Let's try other charts to get familiar with the syntax.

```{r}
data(economics_long, package = "ggplot2")

economics_long2 <- dplyr::filter(economics_long, variable %in% c("pop", "uempmed", "unemploy"))

head(economics_long2)

hchart(economics_long2, "line", hcaes(x = date, y = value01, group = variable))
```

Now, a heatmap and a treemap.

```{r}
library(dplyr)

dfdiam <- diamonds %>% 
  group_by(cut, clarity) %>%
  summarize(price = median(price))

hchart(dfdiam, "heatmap", hcaes(x = cut, y = clarity, value = price), name = "Median Price") 

mpgman <- mpg %>% 
  group_by(manufacturer) %>% 
  summarise(n = n(),
            unique = length(unique(model))) %>% 
  arrange(-n, -unique)

hchart(mpgman, "treemap", hcaes(x = manufacturer, value = n, color = unique))
```

## Extra parameters

You can add other parameters to add options to the data series. This options
can modify the names of each series/group. These names are used in the legend
as well the tooltip. You can modify the colors and a lot of properties.

```{r}
mpgman2 <- count(mpg, manufacturer, year)

hchart(
  mpgman2, 
  "bar",
  hcaes(x = manufacturer, y = n, group = year),
  color = c("#7CB5EC", "#F7A35C"),
  name = c("Year 1999", "Year 2008"),
  showInLegend = c(TRUE, FALSE) # only show the first one in the legend
  )
```

Highcharts has a very complete API with a lot of options. You can 
see every option in action in https://api.highcharts.com/highcharts/plotOptions.series.

## A more advanced example

Using the `broom` package is really nice due the you can transform 
models to tidy data:

```{r, message=FALSE}
library(broom)

modlss <- loess(hwy ~ cty, data = mpg)
fit <- arrange(augment(modlss), cty)

head(fit)
```

In this case we'll chart the original data first and store in a variable called
`hc` (for highcharts):

```{r}
hc <- hchart(
  mpg,
  type = "scatter",
  hcaes(x = cty, y = hwy, group = year)
  )

hc
```

We can add more series to chart (like the layers in ggplot world) using the
function `hc_add_series`. The parameters in this functions are similar to
the `hchart`:


```r
hc_add_series(<highcarter_object>, <data.frame>, <type_of_chart>, hcaes(<aesthetics>), ...)

# or with the pipe:

<highcarter_object> %>% hc_add_series(<data.frame>, <type_of_chart>, hcaes(<aesthetics>), ...)

```

In this case we will add 2 groups of series. The 1st to add will be the 
spline then the arearange. So we'll use `hc_add_series` 2 times.

```{r}
hc %>%
  hc_add_series(
    fit,
    type = "spline",
    hcaes(x = cty, y = .fitted),
    name = "Fit",
    id = "fit", # this is for link the arearange series to this one and have one legend
    lineWidth = 1 
    ) %>% 
  hc_add_series(
    fit,
    type = "arearange",
    name = "SE",
    hcaes(x = cty, low = .fitted - 5*.se.fit, high = .fitted + 5*.se.fit),
    linkedTo = "fit", # here we link the legends in one.
    color = hex_to_rgba("gray", 0.2),  # put a semi transparent color
    zIndex = -3 # this is for put the series in a back so the points are showed first
    )
```

## What now?

Since you know the basics now it could be interesting:

- Go motivate yourself with the `vignette("showcase")` and observe everything that can be 
done with the highcharter package.
- Learn to configure graphics using the implemented API in `vignette("highcharts-api")`.

