---
title: Commons HOW TOs
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  A list of examples of commons _how to_s.
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "question-circle-o"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
```

## Introducction


```{r}
library(highcharter)
library(dplyr)
data(penguins, package = "palmerpenguins")

set.seed(123)

penguins <- palmerpenguins::penguins %>% 
  filter(complete.cases(.)) %>% 
  group_by(species) %>% 
  sample_n(25) %>% 
  ungroup() %>% 
  select(flipper_length_mm, bill_length_mm, species)

glimpse(penguins)

hc <- hchart(penguins, "scatter", hcaes(x = flipper_length_mm, y = bill_length_mm, group = species)) 
hc
```

And:

```{r}
preguins_grouped <- penguins %>% 
  group_by(species) %>% 
  summarise(flipper_length_mm_mean = mean(flipper_length_mm))

glimpse(preguins_grouped)

hc2 <- hchart(preguins_grouped, "column", hcaes(x = species, y = flipper_length_mm_mean))
hc2
```



## Disabled inactive state 

By default, when you hover over a series all the rest are hiding using opacity.
To avoidthis behaviour you can set `opactiy = 1` in the `series.states.inactive`:

```{r}
hc %>%
  hc_plotOptions(
    series = list(states = list(inactive = list(opacity = 1)))
    )
```

More info: https://api.highcharts.com/highcharts/plotOptions.series.states.inactive.

Example: https://jsfiddle.net/gh/get/library/pure/highcharts/highcharts/tree/master/samples/highcharts/plotoptions/series-states-inactive-

## Axis Label Custom Order

Remember `hc2`. If we want a new order we can give the explicit order
using `hc_xAxis`: 

```{r}
lvls <- preguins_grouped %>% 
  mutate(
    species = forcats::fct_relevel(species, "Gentoo", after  = 0)
  ) %>% 
  pull(species) %>% 
  levels()

hchart(preguins_grouped, "column", hcaes(x = species, y = flipper_length_mm_mean)) %>% 
  hc_xAxis(categories = lvls)
```


