---
title: Maps with highmaps
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description:
  libraries from highchartsJS to chart maps, choroplets and geojson.
  The highcharter package include [highmaps](https://www.highcharts.com/demo/maps) 
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Maps with highmaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}    
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "map-o"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, out.width="100%", eval = FALSE)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(), highcharter.download_map_data = TRUE)
```

The highcharter package include [highmaps](https://www.highcharts.com/demo/maps) 
libraries from highchartsJS to chart maps, choropleths and geojson.

## Basics

The easiest way to chart a map with highcharter is using `hcmap()` function.
Select a map (a url) from the highmaps collection 
https://code.highcharts.com/mapdata/.
and use the url as a map in `hcmap()` function. This will download the map
and create a `highchart` object using the info as a `mapData` argument.

Let's try some maps:


```{r, warning=FALSE, message=FALSE}
library(highcharter)
hcmap("countries/nz/nz-all")


hcmap("custom/usa-and-canada", showInLegend = FALSE)

hcmap("countries/us/us-ca-all") |>
  hc_title(text = "California") |> 
  hc_subtitle(text = "You can use the same functions to modify your map!")
```

__Note__: _The copyright information is added to the chart credits by default, 
but please be aware that you will have to display this information somewhere 
else if you choose to disable chart credits. Copyright information for each map
can be found as properties in the GeoJSON and Javascript files_.

## Choropleths

What about add data to get a choropleth? Every map downloaded from the 
highchartsJS maps collection have keys to join data. There are 2 functions
to help to know what are the regions coded to know how to join the map
and data:

- `download_map_data()`: Download the geojson data from the highchartsJS collection.
- `get_data_from_map()`: Get the properties  for each region in the map, as 
the keys from the map data.

```{r}
require(dplyr)

mapdata <- get_data_from_map(download_map_data("custom/usa-and-canada"))

glimpse(mapdata)

data_fake <- mapdata |>
  select(code = `hc-a2`) |>
  mutate(value = 1e5 * abs(rt(nrow(mapdata), df = 10)))

glimpse(data_fake)
```

If we compare this 2 data frames the `hc-key` is same code that
`code`. So we'll use these columns as keys:

```{r}
hcmap(
  "custom/usa-and-canada",
  data = data_fake,
  value = "value",
  joinBy = c("hc-a2", "code"),
  name = "Fake data",
  dataLabels = list(enabled = TRUE, format = "{point.name}"),
  borderColor = "#FAFAFA",
  borderWidth = 0.1,
  tooltip = list(
    valueDecimals = 2,
    valuePrefix = "$",
    valueSuffix = "USD"
  )
)
```

## Categorized areas

```{r}
data <- tibble(
  country = 
    c("PT", "IE", "GB", "IS",
      
      "NO", "SE", "DK", "DE", "NL", "BE", "LU", "ES", "FR", "PL", "CZ", "AT",
      "CH", "LI", "SK", "HU", "SI", "IT", "SM", "HR", "BA", "YF", "ME", "AL", "MK",
      
      "FI", "EE", "LV", "LT", "BY", "UA", "MD", "RO", "BG", "GR", "TR", "CY",
      
      "RU"),  
  tz = c(rep("UTC", 4), rep("UTC + 1",25), rep("UCT + 2",12), "UTC + 3")
  )

# auxiliar variable
data <- data |> 
  mutate(value = cumsum(!duplicated(tz)))


# now we'll create the dataClasses
dta_clss <- data |> 
  mutate(value = cumsum(!duplicated(tz))) |> 
  group_by(tz) |> 
  summarise(value = unique(value)) |> 
  arrange(value) |> 
  rename(name = tz, from = value) |> 
  mutate(to = from + 1) |> 
  list_parse()

hcmap(
  map = "custom/europe",
  data = data, 
  joinBy = c("iso-a2","country"),
  name = "Time zone",
  value = "value",
  tooltip = list(pointFormat = "{point.name} {point.tz}"),
  dataLabels = list(enabled = TRUE, format = "{point.country}")
  ) |>
  hc_colorAxis(
    dataClassColor = "category",
    dataClasses = dta_clss
    ) |> 
  hc_title(text = "Europe Time Zones")
```

Example from https://www.highcharts.com/demo/maps/category-map.

## Adding Points

With highcharter is possible add data as points or bubbles. For this it is 
necessary a data frame with `lat`, `lon` columns, and `name`, `z`  are
optional:

```{r}
cities <- data.frame(
  name = c("London", "Birmingham", "Glasgow", "Liverpool"),
  lat = c(51.507222, 52.483056, 55.858, 53.4),
  lon = c(-0.1275, -1.893611, -4.259, -3),
  z = c(1, 2, 3, 2)
)

hcmap("countries/gb/gb-all", showInLegend = FALSE) |>
  hc_add_series(
    data = cities, 
    type = "mappoint",
    name = "Cities", 
    minSize = "1%",
    maxSize = "5%"
    ) |>
  hc_mapNavigation(enabled = TRUE)

hcmap("countries/gb/gb-all", showInLegend = FALSE) |>
  hc_add_series(
    data = cities, 
    type = "mapbubble",
    name = "Cities", 
    minSize = "1%",
    maxSize = "5%"
    ) |>
  hc_mapNavigation(enabled = TRUE)
```

Another example:


```{r}
library(dplyr)

airports <- read.csv(
  "https://raw.githubusercontent.com/ajdapretnar/datasets/master/data/global_airports.csv",
  stringsAsFactors = FALSE
  )

south_america_countries <- c(
    "Brazil", "Ecuador", "Venezuela",
    "Chile", "Argentina", "Peru",
    "Uruguay", "Paraguay", "Bolivia", 
    "Suriname", "Guyana", "Colombia"
  ) 

airports <- airports |>
  filter(country %in% south_america_countries) |>
  rename(lat = latitude, lon = longitude) |>
  filter(lon < -30)

hcmap(
  "custom/south-america",
  name = "South America",
  showInLegend = FALSE
) |>
  hc_add_series(
    data = airports,
    type = "mappoint",
    name = "Airports",
    color = hex_to_rgba("darkred", alpha = 0.3),
    maxSize = "10",
    tooltip = list(
      pointFormat = "{point.name}: {point.altitude:,.0f} feets <br>
      ({point.lat:,.2f}, {point.lon:,.2f})"
    )
  ) |>
  hc_chart(zoomType = "xy")
```

## `geojsonio` Package

highchartsJS support `geo_json` classes from the `geojsonio` package. So you 
can use `hc_add_series` as usual without use `geojson = TRUE` 
parameter/argument.


```{r}
library(httr)
library(jsonlite)
library(geojsonio)

ausgeojson <- GET("https://raw.githubusercontent.com/johan/world.geo.json/master/countries/AUS.geo.json") |>
  content() |>
  fromJSON(simplifyVector = FALSE) |>
  as.json()

ausmap <- highchart(type = "map") |>
  hc_add_series(mapData = ausgeojson, showInLegend = FALSE)
ausmap
```

We can still adding data:


```{r}
airports <- read.csv("https://raw.githubusercontent.com/ajdapretnar/datasets/master/data/global_airports.csv")
airports <- filter(airports, country == "Australia", name != "Roma Street Railway Station")

airp_geojson <- geojson_json(airports, lat = "latitude", lon = "longitude")
class(airp_geojson)

ausmap |>
  hc_add_series(
    data = airp_geojson,
    type = "mappoint",
    dataLabels = list(enabled = FALSE),
    name = "Airports",
    tooltip = list(pointFormat = "{point.name}")
  )
```

## Advanced Example

Let's download some geojson files and make a map.

```{r, eval=TRUE}
getContent <- function(url) {
  library(httr)
  content(GET(url))
}

world <- getContent("https://raw.githubusercontent.com/johan/world.geo.json/master/countries.geo.json")
# is text
world <- jsonlite::fromJSON(world, simplifyVector = FALSE)

# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_corrientes_maritimas
marine <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_corrientes_maritimas&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# marine <- geojsonio::as.json(marine)


# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_limites_placas
plates <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_limites_placas&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# plates <- geojsonio::as.json(plates)

# http://cedeusdata.geosteiniger.cl/layers/geonode:mundo_volcanes
volcano <- getContent("http://cedeusdata.geosteiniger.cl/geoserver/wfs?srsName=EPSG%3A4326&typename=geonode%3Amundo_volcanes&outputFormat=json&version=1.0.0&service=WFS&request=GetFeature")
# volcano <- geojsonio::as.json(volcano)
```

The data is ready. Remember you can keep using the rest of the API to 
customize your map.

```{r, eval=TRUE}
highchart(type = "map") |>
  hc_chart(backgroundColor = "#161C20") |>
  hc_add_series(
    mapData = world,
    showInLegend = FALSE,
    nullColor = "#424242",
    borderWidth = 0
  ) |>
  hc_add_series(
    data = marine,
    type = "mapline",
    geojson = TRUE,
    color = "#2980b9",
    name = "Marine currents",
    tooltip = list(pointFormat = "{point.properties.NOMBRE}")
  ) |>
  hc_add_series(
    data = plates,
    type = "mapline",
    lineWidth = 2,
    zIndex = -1,
    geojson = TRUE,
    color = "#d35400",
    name = "Plates",
    tooltip = list(pointFormat = "{point.properties.TIPO}")
  ) |>
  hc_add_series(
    data = volcano,
    type = "mappoint",
    color = hex_to_rgba("#f1c40f", 0.4),
    geojson = TRUE,
    name = "Volcanos",
    tooltip = list(pointFormat = "{point.properties.NOMBRE}"),
    marker = list(lineWidth = 0, radius = 2)
  )
```
