---
title: Showcase
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  In this vignette we'll review some examples to show what highcharts and
  highcharter can do in terms of customization and design.
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Showcase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}    
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "newspaper-o"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, out.width="100%")
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
```

In this vignette we'll review some examples to show what highcharts and
highcharter can do in terms of customization and design.

## HIMYM example

> This is a bar graph describing my favorite pies including a pie chart describing my favorite bars.
> - _Marshall Eriksen_

```{r bar}
data(favorite_bars)
data(favorite_pies)

highchart() |> 
  # Data
  hc_add_series(
    favorite_pies, 
    "column",
    hcaes(
      x = pie,
      y = percent
      ),
    name = "Pie"
    ) |>
  hc_add_series(
    favorite_bars,
    "pie",
    hcaes(
      name = bar,
      y = percent
      ),
    name = "Bars"
    ) |>
  # Options for each type of series
  hc_plotOptions(
    series = list(
      showInLegend = FALSE,
      pointFormat = "{point.y}%",
      colorByPoint = TRUE
      ),
    pie = list(
      center = c('30%', '10%'),
      size = 120,
      dataLabels = list(enabled = FALSE)
      )
    ) |>
  # Axis
  hc_yAxis(
    title = list(text = "percentage of tastiness"),
    labels = list(format = "{value}%"), 
    max = 100
  ) |> 
  hc_xAxis(
    categories = favorite_pies$pie
    ) |>
  # Titles, subtitle, caption and credits
  hc_title(
    text = "How I Met Your Mother: Pie Chart Bar Graph"
  ) |> 
  hc_subtitle(
    text = "This is a bar graph describing my favorite pies
    including a pie chart describing my favorite bars"
  ) |>
  hc_caption(
    text = "The values represented are in percentage of tastiness and awesomeness."
    ) |> 
  hc_credits(
    enabled = TRUE, text = "Source: HIMYM",
    href = "https://www.youtube.com/watch?v=f_J8QU1m0Ng",
    style = list(fontSize = "12px")
  ) |> 
  hc_size(
    height = 600
    )
```


## Pokemon

```{r pokemon}
library(dplyr)
data(pokemon)

lvl_opts <-  list(
    list(
      level = 1,
      borderWidth = 0,
      borderColor = "transparent",
      dataLabels = list(
        enabled = TRUE,
        align = "left",
        verticalAlign = "top",
        style = list(
          fontSize = "12px", 
          textOutline = FALSE,
          color = "white",
          fontWeight = "normal"
          )
      )
    ),
    list(
      level = 2,
      borderWidth = 0,
      borderColor = "transparent",
      colorVariation = list(key = "brightness", to = 0.250),
      dataLabels = list(enabled = FALSE),
      style = list(
        fontSize = "8px",
        textOutline = FALSE, 
        color = "white", 
        fontWeight = "normal"
        )
    )
  )

pkmn_min <- pokemon |> 
  select(type_1, type_2, type_1_color) |>
  mutate(type_1 = stringr::str_to_title(type_1)) |> 
  mutate(type_2 = ifelse(is.na(type_2), type_1, paste(type_1, "-", type_2))) |>
  mutate(val = 1)

cols <- pkmn_min |> 
  count(type_1, type_2, type_1_color, sort = TRUE) |> 
  pull(type_1_color) |> 
  unique()

hchart(
  data_to_hierarchical(pkmn_min, c(type_1, type_2), val, colors = cols),
  type = "treemap",
  # levelIsConstant = FALSE,
  allowDrillToNode = TRUE,
  levels = lvl_opts,
  tooltip = list(valueDecimals = FALSE)
  ) |> 
  hc_chart(
    style = list(fontFamily = "Gloria Hallelujah")
  ) |> 
  hc_title(
    text = "Gotta Catch 'Em All!",
    style = list(fontFamily = "Gloria Hallelujah")
    ) |> 
  hc_size(height = 700)
```


## Weathers Radials

Example inspired by http://weather-radials.com/.

```{r weather}
library(highcharter)
data(weather)

x <- c("Min", "Mean", "Max")
y <- sprintf("{point.%s}°", c("min_temperaturec", "mean_temperaturec", "max_temperaturec"))

tltip <- tooltip_table(x, y)

hchart(
  weather,
  type = "columnrange",
  hcaes(
    x = date, 
    low = min_temperaturec, 
    high = max_temperaturec,
    color = mean_temperaturec
    )
  ) |>
  hc_chart(
    polar = TRUE
    ) |>
  hc_yAxis(
    max = 30,
    min = -10,
    labels = list(format = "{value} C"),
    showFirstLabel = FALSE
  ) |>
  hc_xAxis(
    title = list(text = ""), 
    gridLineWidth = 0.5,
    labels = list(format = "{value: %b}")
  ) |>
  hc_tooltip(
    useHTML = TRUE,
    pointFormat = tltip,
    headerFormat = as.character(tags$small("{point.x:%d %B, %Y}"))
  ) |> 
  hc_title(
    text = "Climatical characteristics of San Francisco"
  ) |> 
  hc_size(
    height = 600
  )
```

## Stars

Inspired by Nadieh Bremer's [block](http://bl.ocks.org/nbremer/eb0d1fd4118b731d069e2ff98dfadc47).

```{r stars}
data(stars)

colors <- c(
  "#FB1108", "#FD150B", "#FA7806", "#FBE426", "#FCFB8F",
  "#F3F5E7", "#C7E4EA", "#ABD6E6", "#9AD2E1"
)

stars$color <- highcharter::colorize(log(stars$temp), colors)

x <- c("Luminosity", "Temperature", "Distance", "Radius")
y <- sprintf("{point.%s:.2f}", c("lum", "temp", "distance", "radiussun"))

tltip <- tooltip_table(x, y)

hchart(
  stars,
  "scatter",
  hcaes(
    temp, 
    lum, 
    size = radiussun, 
    color = color
    ),
  minSize = 2,
  maxSize = 20
  ) |>
  hc_chart(
    # backgroundColor = "black"
    backgroundColor = hex_to_rgba("black", 0.5),
    divBackgroundImage = "http://www.wired.com/images_blogs/underwire/2013/02/xwing-bg.gif"
    ) |>
  hc_xAxis(
    title = list(text = "Temperature"),
    type = "logarithmic",
    gridLineWidth = 0,
    reversed = TRUE
    ) |>
  hc_yAxis(
    title = list(text = "Luminosity"),
    type = "logarithmic", 
    gridLineWidth = 0
    ) |>
  hc_title(
    style = list(color = hex_to_rgba("white", 0.5)),
    text = "Our nearest Stars"
    ) |>
  hc_subtitle(
    style = list(color = hex_to_rgba("white", 0.5)),
    text = "In a Hertzsprung-Russell diagram"
    ) |>
  hc_tooltip(
    useHTML = TRUE,
    headerFormat = "",
    pointFormat = tltip
    ) |>
  hc_size(
    height = 700
    )
```

## The Impact of Vaccines

From [WSJ graphic: Battling Infectious Diseases in the 20th Century](http://graphics.wsj.com/infectious-diseases-and-vaccines/): 

```{r vaccines}
data(vaccines)

fntltp <- JS("function(){
  return this.point.x + ' ' +  this.series.yAxis.categories[this.point.y] + ': ' +
  Highcharts.numberFormat(this.point.value, 2);
}")

plotline <- list(
  color = "#fde725", value = 1963, width = 2, zIndex = 5,
  label = list(
    text = "Vaccine Intoduced", verticalAlign = "top",
    style = list(color = "#606060"), textAlign = "left",
    rotation = 0, y = -5
  )
)

hchart(
  vaccines, 
  "heatmap", 
  hcaes(
    x = year,
    y = state, 
    value = count
    )
  ) |>
  hc_colorAxis(
    stops = color_stops(10, viridisLite::inferno(10, direction = -1)),
    type = "logarithmic"
  ) |>
  hc_yAxis(
    title = list(text = ""),
    reversed = TRUE, 
    offset = -20,
    tickLength = 0,
    gridLineWidth = 0, 
    minorGridLineWidth = 0,
    labels = list(style = list(fontSize = "9px"))
  ) |>
  hc_tooltip(
    formatter = fntltp
    ) |>
  hc_xAxis(
    plotLines = list(plotline)) |>
  hc_title(
    text = "Infectious Diseases and Vaccines"
    ) |>
  hc_subtitle(
    text = "Number of cases per 100,000 people"
  ) |> 
  hc_legend(
    layout = "horizontal",
    verticalAlign = "top",
    align = "left",
    valueDecimals = 0
  ) |>
  hc_size(height = 1000)
```

