---
title: Stocks with highstocks
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  libraries from highchartsJS to create stock or general timeline charts.
  Features sophisticated navigation for high-volume data, user annotations and
  range selectors.
  The highcharter package include [highstocks](https://www.highcharts.com/demo/stock)
editor_options: 
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Stocks with highstocks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}   
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "line-chart"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
library(highcharter)
options(highcharter.theme = hc_theme_hcrt(tooltip = list(valueDecimals = 2)))
```

The highcharter package include [highstocks](https://www.highcharts.com/demo/stock) 
libraries from highchartsJS to create stock or general timeline charts.
Features sophisticated navigation for high-volume data, user annotations and
range selectors.

## Basics

Highstock work well with the quantmod package. It's  easy chart symbols using
`hchart()`. Then you can add more series using `hc_add_series()`.

```{r}
library(quantmod)

x <- getSymbols("GOOG", auto.assign = FALSE)

hchart(x)
```

Obviously you can use the implemented API functions to edit the chart:

```{r}
y <- getSymbols("AMZN", auto.assign = FALSE)

hchart(y, type = "ohlc") |> 
  hc_title(text = "This is a Open-high-low-close chart with a custom theme") |> 
  hc_add_theme(hc_theme_db())
```

## Candlestick and OHLC charts

If you want to chart more symbols in you can
use the `hc_add_series()` function. Don't forget to specify `type = "stock"` to
activate the navigator, range selector and other features of highstock.   

```{r}
hc <- highchart(type = "stock") |> 
  hc_add_series(x, id = 1) |> 
  hc_add_series(y, type = "ohlc", id = 2)

hc
```
## Flags

Previously we used the `id` parameter. This is necessary 
to add flags to relate series and flags:

```{r}
library(dplyr)

set.seed(123)

data_flags <- tibble(
  date = sample(time(x), size = 5),
  title = sprintf("E #%s", seq_along(date)),
  text = sprintf("An interesting event #%s in %s", seq_along(date), date)
)

glimpse(data_flags)

hc |> 
  hc_add_series(
    data_flags, 
    hcaes(x = date),
    type = "flags", 
    onSeries = 2
    )
```

## Advanced Example

You can do what you want. Use all the highchartsJS API to add axis, series, 
bands, etc.

```{r}
SPY <- getSymbols("SPY", from = Sys.Date() - lubridate::years(1), auto.assign = FALSE)
SPY <- adjustOHLC(SPY)

SPY.SMA.10 <- SMA(Cl(SPY), n = 5)
SPY.SMA.200 <- SMA(Cl(SPY), n = 100)
SPY.RSI.14 <- RSI(Cl(SPY))
SPY.RSI.SellLevel <- xts(rep(70, NROW(SPY)), index(SPY))
SPY.RSI.BuyLevel <- xts(rep(30, NROW(SPY)), index(SPY))


highchart(type = "stock") |> 
  # create axis :)
  hc_yAxis_multiples(create_yaxis(3, height = c(2, 1, 1), turnopposite = TRUE)) |> 
  # series :D
  hc_add_series(SPY, yAxis = 0, name = "SPY") |> 
  hc_add_series(SPY.SMA.10, yAxis = 0, name = "Fast MA") |> 
  hc_add_series(SPY.SMA.200, yAxis = 0, name = "Slow MA") |> 
  hc_add_series(SPY$SPY.Volume, color = "gray", yAxis = 1, name = "Volume", type = "column") |> 
  hc_add_series(SPY.RSI.14, yAxis = 2, name = "Osciallator", color = hex_to_rgba("green", 0.7)) |>
  hc_add_series(SPY.RSI.SellLevel, color = hex_to_rgba("red", 0.7), yAxis = 2, name = "Sell level") |> 
  hc_add_series(SPY.RSI.BuyLevel, color = hex_to_rgba("blue", 0.7), yAxis = 2, name = "Buy level") |> 
  hc_tooltip(valueDecimals = 2) |> 
  hc_size(height = 800)
```

