---
title: Themes
author: Joshua Kunst
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: >
  Highcharts is very flexible for create or themes.
  In Highcarter there are some predefined themes and some 
  functions to create your own or merge themes.
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "paint-brush"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(highcharter)
library(dplyr)
library(htmltools)
library(ggplot2)
```

Highcharts is very flexible for create or themes.
In Highcarter there are some predefined themes and some 
functions to create your own or merge themes.

Let's start with a simple bar chart and see the default theme:

```{r}
library(highcharter)
library(dplyr)

data(diamonds, package = "ggplot2")

data <- count(diamonds, cut, color)

hc <- hchart(data, "column", hcaes(x = color, y = n, group = cut)) %>%
  hc_yAxis(title = list(text = "Cases")) %>%
  hc_title(text = "Diamonds Are Forever") %>%
  hc_subtitle(text = "Source: Diamonds data set") %>%
  hc_credits(enabled = TRUE, text = "http://jkunst.com/highcharter/") %>%
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_caption(text = "This is a caption text to show the style of this type of text")

hc
```


## Themes

Here you'll find the themes to change the look of your charts.

```{r, echo=FALSE}
library(tidyverse)

# themes <- help.search("theme", package = "highcharter") %>%
#   .$matches %>%
#   tibble::as_tibble() %>%
#   janitor::clean_names() %>%
#   select(name, title) %>%
#   distinct() %>%
#   filter(str_detect(name, "hc_theme_*")) %>%
#   filter(!name %in% c("hc_theme_merge", "hc_theme")) %>%
#   mutate(title = str_replace(title, " theme for highcharts", "")) %>%
#   arrange(name)

# themes <- dir("R", full.names = TRUE) %>%
#   str_subset("theme") %>%
#   setdiff("R/theme.R") %>%
#   map(readLines) %>%
#   reduce(c) %>%
#   str_subset(" <- function") %>%
#   str_remove(" <-.*")
# 
# dput(themes)

themes <- c("hc_theme_538", "hc_theme_alone", "hc_theme_bloom", "hc_theme_chalk", 
"hc_theme_darkunica", "hc_theme_db", "hc_theme_economist", "hc_theme_elementary", 
"hc_theme_ffx", "hc_theme_flat", "hc_theme_flatdark", "hc_theme_ft", 
"hc_theme_ggplot2", "hc_theme_google", "hc_theme_gridlight", 
"hc_theme_handdrawn", "hc_theme_hcrt", "hc_theme_monokai", "hc_theme_null", 
"hc_theme_sandsignika", "hc_theme_smpl", "hc_theme_sparkline", 
"hc_theme_sparkline_vb", "hc_theme_superheroes", "hc_theme_tufte", 
"hc_theme_tufte2")

themes <- str_subset(themes, "spark", negate = TRUE)

thms <- unique(c("hc_theme_smpl", "hc_theme_db", themes))
# thms <- sample(thms, 5)

# generate tabs
thms %>%
  map(function(t) { # t <- sample(thms, 1)

    t %>%
      str_replace_all("hc_theme_", "") %>%
      tags$a(`data-target` = paste0("#", t), `data-toggle` = "tab") %>%
      tags$li(class = if (t == thms[1]) "active" else NULL)
  }) %>%
  tags$ul(class = "nav nav-pills", id = "myTab", .)


tags$br()

thms %>%
  map(function(t) { # t <- sample(thms, 1)

    thm <- get(t)()

    content <- list(hc) %>%
      map(hc_add_theme, thm)

    tags$div(content, id = t, class = "tab-pane", class = if (t == thms[1]) "active" else NULL)
  }) %>%
  tags$div(class = "tab-content")
```


## Creating themes

You can create your own themes!

```{r}
my_own_theme <- hc_theme(
  colors = c("red", "green", "blue"),
  chart = list(
    backgroundColor = NULL,
    divBackgroundImage = "http://media3.giphy.com/media/FzxkWdiYp5YFW/giphy.gif"
  ),
  title = list(
    style = list(
      color = "#333333",
      fontFamily = "Lato"
    )
  ),
  subtitle = list(
    style = list(
      color = "#666666",
      fontFamily = "Shadows Into Light"
    )
  ),
  legend = list(
    itemStyle = list(
      fontFamily = "Tangerine",
      color = "black"
    ),
    itemHoverStyle = list(
      color = "gray"
    )
  )
)

hc %>%
  hc_add_theme(my_own_theme)
```

## Merge Themes

You can merge themes too.

```{r}
thm <- hc_theme_merge(
  hc_theme_darkunica(),
  hc_theme(
    chart = list(
      backgroundColor = "transparent",
      divBackgroundImage = "http://www.wired.com/images_blogs/underwire/2013/02/xwing-bg.gif"
    ),
    title = list(
      style = list(
        color = "white",
        fontFamily = "Griffy",
        fontSize = "25px"
      )
    )
  )
)

hc %>%
  hc_add_theme(thm)
```
