---
title: "`hchart` function"
output: html_document
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "magic-o"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
library(highcharter)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
options(download.file.method = "libcurl")
```

The `hchart` function is generic, this means you can chart various R objects 
on the fly. The resulting chart is a highchart object
so you can keep modifying with the implmented API.

## Data Frames

This function works like `qplot`: You pass the data, choose the type
of chart and then define the aesthetics for each variable.

```{r}
library(highcharter)
library(dplyr)

data(diamonds, economics_long, mpg, package = "ggplot2")

hchart(mpg, "scatter", hcaes(x = displ, y = hwy, group = class))

mpgman2 <- mpg %>%
  count(class, year) %>%
  glimpse()

hchart(mpgman2, "column", hcaes(x = class, y = n, group = year))
```

Check automatically if the x column is date class:

```{r}
economics_long2 <- economics_long %>%
  filter(variable %in% c("pop", "uempmed", "unemploy"))

hchart(economics_long2, "line", hcaes(x = date, y = value01, group = variable))
```

## Numeric & Histograms

```{r}
x <- diamonds$price
hchart(x)
```

## Densities

```{r}
hchart(density(x), type = "area", color = "#B71C1C", name = "Price")
```

## Character & Factor

```{r}
x <- diamonds$cut
hchart(x, type = "column")
```

## Time Series

```{r}
hchart(LakeHuron)
```

## Seasonal Decomposition of Time Series by Loess

```{r}
x <- stl(log(AirPassengers), "per")
hchart(x)
```

## Forecast package

```{r}
library(forecast)

x <- forecast(ets(USAccDeaths), h = 48, level = 95)
hchart(x)
```

## Igraph package

```{r}
library(igraph)
N <- 40

net <- sample_gnp(N, p = 2 / N)
wc <- cluster_walktrap(net)

V(net)$label <- seq(N)
V(net)$name <- paste("I'm #", seq(N))
V(net)$page_rank <- round(page.rank(net)$vector, 2)
V(net)$betweenness <- round(betweenness(net), 2)
V(net)$degree <- degree(net)
V(net)$size <- V(net)$degree
V(net)$comm <- membership(wc)
V(net)$color <- colorize(membership(wc))

hchart(net, layout = layout_with_fr)
```

## Survival Package

Survival models can be charted.

```{r}
library(survival)

data(lung)
lung <- mutate(lung, sex = ifelse(sex == 1, "Male", "Female"))
fit <- survfit(Surv(time, status) ~ sex, data = lung)

hchart(fit, ranges = TRUE)
```

## Quantmod package

The highstock extension is used to chart `xts` and `xts ohlc` classes from the
quantmod package. 

```{r}
library(quantmod)

x <- getFX("USD/JPY", auto.assign = FALSE)
hchart(x)

y <- getSymbols("SPY", auto.assign = FALSE)
hchart(y)
```

## Multivariate Time series

```{r}
x <- cbind(mdeaths, fdeaths)
hchart(x)
```

## Autocovariance & Autocorrelation

```{r}
x <- acf(diff(AirPassengers), plot = FALSE)
hchart(x)
```


## Principal Components

```{r}
hchart(princomp(USArrests, cor = TRUE))
```

## Matrix

```{r}
data(volcano)
hchart(volcano) %>% # changing default color
  hc_colorAxis(stops = color_stops(colors = viridis::inferno(10)))
```

## Distance matrix 

```{r}
mtcars2 <- mtcars[1:20, ]
x <- dist(mtcars2)
hchart(x)
```

## Correlation matrix

```{r}
hchart(cor(mtcars))
```
