---
title: "Highcharts API"
author: "Joshua Kunst"
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "cogs"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r echo=FALSE, warning=FALSE, message=FALSE}
rm(list = ls())
library(highcharter)
options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
```

Highcharts have a rich API which allows you to have control of the entire chart, from title, subtitle to
axis ticks, labels, annotations. We'll review all the functions to control the chart.

*Premise*: There's not default arguments. All arguments need to be named.


# Title, subtitle, caption and credits

Fist of all, let's create a simple chart:

```{r}
data(mpg, package = "ggplot2")
library(dplyr)
library(highcharter)

mpgc <- mpg %>% 
  count(year, class)

hc <- hchart(mpgc, "column", hcaes(class, n, group = year))
hc
```

A good chart always have at least title, right? Then you can do it better adding relevant information
using a subtitle or caption, even link to the source of data:

```{r}
hc %>% 
  hc_title(text = "This is the title of the chart") %>% 
  hc_subtitle(text = "This is an intereseting subtitle to give context for the chart or some interesting fact") %>% 
  hc_caption(text = "This is a long text to give some 
subtle details of the data which can be relevant to the reader. This is usually a long text
that's why I'm trying to put a <i>loooooong</i> text.", useHTML = TRUE) %>% 
  hc_credits(text = "Chart created using R and highcharter", href = "http://jkunst.com/highcharter", enabled = TRUE)
```

# Axis

Usually is deseable get control and modiy the axis:

```{r}
data("citytemp_long")

hc2 <- hchart(citytemp_long, "line", hcaes(month, temp, group = city))
hc2
```

```{r}
hc2 %>% 
  hc_xAxis(
    title = list(text = "Month in x Axis"),
    opposite = TRUE
    ) %>% 
  hc_yAxis(
    title = list(text = "Temperature <b>in y Axis</b>", useHTML = TRUE),
    opposite = TRUE,
    minorTickInterval = "auto",
    minorGridLineDashStyle = "LongDashDotDot",
    showFirstLabel = FALSE,
    showLastLabel = FALSE
  )
```

A good feature is `plotLines` and `plotBand` which you can use in both axis. For example:

```{r}
hc2 %>% 
  hc_xAxis(
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 5.5)
      )
    ) %>% 
  hc_yAxis(
    plotBands = list(
      list(
        from = 20,
        to = 50,
        color = "rgba(100, 0, 0, 0.1)",
        label = list(text = "This is a plotBand")
        )
      )
    ) 
```

       


