---
title: "Highcharts API"
author: "Joshua Kunst"
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "cogs"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r echo=FALSE, warning=FALSE, message=FALSE}
rm(list = ls())
library(highcharter)
options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
```

Highcharts have a rich API which allows you to have control of the entire chart, from title, subtitle to
axis ticks, labels, annotations. We'll review all the functions to control the chart.

*Premise*: There's not default arguments. All arguments need to be named.

Fist of all, let's create a simple chart:


```{r }
data(mpg, package = "ggplot2")
library(dplyr)
library(highcharter)

mpgc <- mpg %>% 
  count(year, class)

hc <- hchart(mpgc, "column", hcaes(class, n, group = year))
hc
```

# Title, subtitle, caption and credits

asd

```{r}
hc %>% 
  hc_title(text = "This is the title of the chart") %>% 
  hc_subtitle(text = "This is an intereseting subtitle to give context for the chart or some interesting fact") %>% 
  hc_caption(text = "This is a long text to give some 
subtle details of the data which can be relevant to the reader. This is usually a long text
that's why I'm trying to put a <i>loooooong</i> text.", useHTML = TRUE) %>% 
  hc_credits(text = "by Joshua Kunst", href = "http://jkunst.com", enabled = TRUE)
```
