---
title: Showcase
output: html_document
editor_options: 
  chunk_output_type: console
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "newspaper-o"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

Let's see some motivational (I hope so) examples!

## Stars Wars

A starting example:

```{r}
library(highcharter)
library(tidyverse)
library(rwars)

swmovies <- get_all_films()

swdata <- map_df(swmovies$results, function(x) {
  data_frame(
    movie = x$title,
    species = length(x$species),
    planets = length(x$planets),
    characters = length(x$characters),
    vehicles = length(x$vehicles),
    release = x$release_date
  )
})

swdata <- gather(swdata, key, number, -movie, -release) %>%
  arrange(release)

hchart(
  swdata,
  "line",
  hcaes(x = movie, y = number, group = key),
  color = c("#e5b13a", "#4bd5ee", "#4AA942", "#FAFAFA")
) %>%
  hc_title(
    text = "Diversity in <span style=\"color:#e5b13a\"> STAR WARS</span> movies",
    useHTML = TRUE
  ) %>%
  hc_tooltip(
    table = TRUE,
    sort = TRUE
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "Source: SWAPI via rwars package",
    href = "https://swapi.co/"
  ) %>%
  hc_add_theme(
    hc_theme_flatdark(
      chart = list(
        backgroundColor = "transparent",
        divBackgroundImage = "http://www.wired.com/images_blogs/underwire/2013/02/xwing-bg.gif"
      )
    )
  )
```


## Stars

Inspired by Nadieh Bremer's [block](http://bl.ocks.org/nbremer/eb0d1fd4118b731d069e2ff98dfadc47).

```{r}
data(stars)

colors <- c(
  "#FB1108", "#FD150B", "#FA7806", "#FBE426", "#FCFB8F",
  "#F3F5E7", "#C7E4EA", "#ABD6E6", "#9AD2E1"
)

stars$color <- colorize(log(stars$temp), colors)

x <- c("Luminosity", "Temperature", "Distance")
y <- sprintf("{point.%s:.2f}", c("lum", "temp", "distance"))
tltip <- tooltip_table(x, y)

hchart(stars, "scatter", hcaes(temp, lum, size = radiussun, color = color)) %>%
  hc_chart(backgroundColor = "black") %>%
  hc_xAxis(type = "logarithmic", gridLineWidth = 0, reversed = TRUE) %>%
  hc_yAxis(type = "logarithmic", gridLineWidth = 0) %>%
  hc_title(text = "Our nearest Stars") %>%
  hc_subtitle(text = "In a Hertzsprung-Russell diagram") %>%
  hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip) %>%
  hc_size(height = 600)
```

## Global temperatures

```{r}
data(globaltemp)

x <- c("Min", "Median", "Max")
y <- sprintf("{point.%s}", c("lower", "median", "upper"))
tltip <- tooltip_table(x, y)

hchart(
  globaltemp,
  type = "columnrange",
  hcaes(x = date, low = lower, high = upper, color = median)
) %>%
  hc_yAxis(
    tickPositions = c(-2, 0, 1.5, 2),
    gridLineColor = "#B71C1C",
    labels = list(format = "{value} C", useHTML = TRUE)
  ) %>%
  hc_tooltip(
    useHTML = TRUE,
    headerFormat = as.character(tags$small("{point.x: %Y %b}")),
    pointFormat = tltip
  ) %>%
  hc_add_theme(hc_theme_db())
```


## Weathers Radials

From [here](http://bl.ocks.org/bricedev/458a01917183d98dff3c) and 
replicated in http://jkunst.com/r/how-to-weather-radials/

```{r}
data(weather)

x <- c("Min", "Mean", "Max")
y <- sprintf("{point.%s}", c("min_temperaturec", "mean_temperaturec", "max_temperaturec"))
tltip <- tooltip_table(x, y)

hchart(weather,
  type = "columnrange",
  hcaes(
    x = date, low = min_temperaturec, high = max_temperaturec,
    color = mean_temperaturec
  )
) %>%
  hc_chart(polar = TRUE) %>%
  hc_yAxis(
    max = 30, min = -10,
    labels = list(format = "{value} C"),
    showFirstLabel = FALSE
  ) %>%
  hc_xAxis(
    title = list(text = ""), gridLineWidth = 0.5,
    labels = list(format = "{value: %b}")
  ) %>%
  hc_tooltip(
    useHTML = TRUE, pointFormat = tltip,
    headerFormat = as.character(tags$small("{point.x:%d %B, %Y}"))
  )
```

## The Impact of Vaccines

From [WSJ graphic: Battling Infectious Diseases in the 20th Century](http://graphics.wsj.com/infectious-diseases-and-vaccines/): 

```{r}
data(vaccines)
library(viridis)

fntltp <- JS("function(){
  return this.point.x + ' ' +  this.series.yAxis.categories[this.point.y] + ':<br>' +
  Highcharts.numberFormat(this.point.value, 2);
}")

plotline <- list(
  color = "#fde725", value = 1963, width = 2, zIndex = 5,
  label = list(
    text = "Vaccine Intoduced", verticalAlign = "top",
    style = list(color = "#606060"), textAlign = "left",
    rotation = 0, y = -5
  )
)

hchart(vaccines, "heatmap", hcaes(x = year, y = state, value = count)) %>%
  hc_colorAxis(
    stops = color_stops(10, rev(inferno(10))),
    type = "logarithmic"
  ) %>%
  hc_yAxis(
    reversed = TRUE, offset = -20, tickLength = 0,
    gridLineWidth = 0, minorGridLineWidth = 0,
    labels = list(style = list(fontSize = "8px"))
  ) %>%
  hc_tooltip(formatter = fntltp) %>%
  hc_xAxis(plotLines = list(plotline)) %>%
  hc_title(text = "Infectious Diseases and Vaccines") %>%
  hc_legend(
    layout = "vertical", verticalAlign = "top",
    align = "right", valueDecimals = 0
  ) %>%
  hc_size(height = 800)
```
