---
title: "Themes"
author: "Joshua Kunst"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script>
$(document).ready(function(){ 
  el = $(".page-header > h1")
  icon = "pencil"
  text = el.text()
  text_new = "<span class=\"fa fa-" + icon  + "\"></span> " + text
  el.html(text_new) 
}) ;
</script>

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(highcharter)
library(dplyr)
library(htmltools)
library(ggplot2)
```

Highcharts is super flexible to add and create themes.
In Highcarter there are some predefined themes and some 
functions to create or merge themes.

Let's start with a simple bar chart and see the defaul theme:

```{r}
library(highcharter)
library(dplyr)
data(diamonds, package = "ggplot2")

data <- count(diamonds, cut, color)
hc <- hchart(data, "column", hcaes(x = color, y = n, group = cut)) %>%
  hc_yAxis(title = list(text = "Cases")) %>%
  hc_title(text = "Diamonds Are Forever") %>%
  hc_subtitle(text = "Source: Diamonds data set") %>%
  hc_credits(enabled = TRUE, text = "jkunst.com") %>%
  hc_tooltip(sort = TRUE, table = TRUE)
hc
```


## Themes

Here you'll find the themes to change the look of your charts.

```{r, echo=FALSE}
library(tidyverse)
themes <- help.search("theme", package = "highcharter") %>%
  .$matches %>%
  tbl_df() %>%
  janitor::clean_names() %>%
  select(name, title) %>%
  distinct() %>%
  filter(str_detect(name, "hc_theme_*")) %>%
  filter(!name %in% c("hc_theme_merge", "hc_theme")) %>%
  mutate(title = str_replace(title, " theme for highcharts", "")) %>%
  arrange(name)

thms <- unique(c("hc_theme_smpl", "hc_theme_db", themes$name))
# thms <- sample(thms, 5)

# generate tabs
thms %>%
  map(function(t) { # t <- sample(thms, 1)

    t %>%
      str_replace_all("hc_theme_", "") %>%
      tags$a(`data-target` = paste0("#", t), `data-toggle` = "tab") %>%
      tags$li(class = if (t == thms[1]) "active" else NULL)
  }) %>%
  tags$ul(class = "nav nav-pills", id = "myTab", .)


tags$br()

thms %>%
  map(function(t) { # t <- sample(thms, 1)

    thm <- get(t)()

    content <- list(hc) %>%
      map(hc_add_theme, thm)

    tags$div(content, id = t, class = "tab-pane", class = if (t == thms[1]) "active" else NULL)
  }) %>%
  tags$div(class = "tab-content")
```


## Creating themes

You can create your own themes!

```{r}
my_own_theme <- hc_theme(
  colors = c("red", "green", "blue"),
  chart = list(
    backgroundColor = NULL,
    divBackgroundImage = "http://media3.giphy.com/media/FzxkWdiYp5YFW/giphy.gif"
  ),
  title = list(
    style = list(
      color = "#333333",
      fontFamily = "Lato"
    )
  ),
  subtitle = list(
    style = list(
      color = "#666666",
      fontFamily = "Shadows Into Light"
    )
  ),
  legend = list(
    itemStyle = list(
      fontFamily = "Tangerine",
      color = "black"
    ),
    itemHoverStyle = list(
      color = "gray"
    )
  )
)

hc %>%
  hc_add_theme(my_own_theme)
```

## Merge Themes

You can merge themes too.

```{r}
thm <- hc_theme_merge(
  hc_theme_darkunica(),
  hc_theme(
    chart = list(
      backgroundColor = "transparent",
      divBackgroundImage = "http://cdn.wall-pix.net/albums/art-3Dview/00025095.jpg"
    ),
    title = list(
      style = list(
        color = "white",
        fontFamily = "Open Sans"
      )
    )
  )
)

hc %>%
  hc_add_theme(thm)
```
